Total Score

### 2023-02-06 src/MSAtotal_scores.Rmd
Changing axis labels on bar chart almost finalized!

```{r data viz}
## read in weighted criteria sheet
weighted_criteria <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "wtd_criteria_Owen")

score_tidy <- weighted_criteria %>% 
  pivot_longer(cols = c(4:9), # selecting criteria cols
               names_to = "criteria",
               values_to = "criteria_score") %>% 
 filter(city_msa != "Portland") # removing portland (negative number)

ggplot(data = score_tidy, aes(y = reorder(cbsa, FINAL_owen_SCORE), x = criteria_score, fill = criteria_labels)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score (Client)",
       y = " ") +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
scale_fill_discrete(labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Finances", "Real Estate", "Landlord")) +
   scale_fill_manual(values = c("#FDB462", "gold", "palevioletred1",  "#BC80BD", "#6699CC", "#44AA99"))

>>>>

```{r data viz}
## read in weighted criteria sheet
weighted_criteria <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "wtd_criteria_Owen") %>% 
  unite("msa_state", city_msa:state, sep = ", ")

# read in cbsa data with full names
score_tidy <- weighted_criteria %>% 
  pivot_longer(cols = c("WT_real_estate":"WT_climRisk"), # selecting criteria cols
               names_to = "criteria",
               values_to = "criteria_score") %>% 
 filter(msa_state != "Portland, ME") %>%  # removing portland (negative number)
  group_by(cbsa)

ggplot(data = score_tidy, aes(y = reorder(msa_state, FINAL_owen_SCORE), x = criteria_score)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score (Client)",
       y = " ") +
  theme_light() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","#FDB462",  "gold", "#44AA99", "dodgerblue4", "#BC80BD"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Finances", "Real Estate", "Landlord Policy"))
